Stats Project 2

### 2022-12-12 article.Rmd
add plots to article

```{r}
plot(t1fit)
```

@@

>>>>

```{r}
plot(fit_numeric)
```
```{r}
plot(transformed_fit) 
```

@@

```{r}
#I'm not sure if this is the best way to do it, but it highlights the requirement of the transform

boxplot(numeric_housing) #<-visualize outliers

#filtered_nh = numeric_housing[-c(692, 1183, 314, 336, 256, 707), ] #filters out outliers 
#filtered_nh$SalePrice = log(filtered_nh$SalePrice) 
#filtered_nh$LotArea = log(filtered_nh$LotArea)

transformed_numeric = numeric_housing
transformed_numeric$SalePrice = log(transformed_numeric$SalePrice)
transformed_numeric$LotArea = log(transformed_numeric$LotArea)
transformed_numeric$GrLivArea = log(transformed_numeric$GrLivArea)

boxplot(transformed_numeric)

transformed_fit = lm(SalePrice ~., data = transformed_numeric)

transForward = ols_step_forward_p(transformed_fit, penter = 0.05, details = FALSE)

transForward
summary(transForward$model)
ModelRMSE(transForward$model$residuals) #see defined functions at top of document
CVPress(transForward$model)
